Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-01-29 paper/ijcai16.tex
paper: donepdflatex ijcai16 still little room for future work

Substituting the above MILP constraints into the original non-linear
formulation, we obtain the following mixed-integer linear problem:
%
{\footnotesize
\begin{align}
    \max
        & \;\; \mu - \alpha \sum_{i=1}^k \| \veps^{i} \|_1 - \beta \sum_{i=1}^k \| \vw^{i} \|_1 + \gamma \sum_{i=1}^k \sum_{z=1}^m p^{i,i}_z
        \nonumber
    \\
    \text{s.t.}
        & \;\; \forall \; i \in [k], \forall \; h \in [n] \quad \langle \vw^{i}, \vy^{h}_+ - \vy^{h}_- \rangle \ge \mu - \varepsilon^{i}_h \nonumber
    \\
        & \;\; \forall \; i, j \in [k], i \neq j \quad \sum_{z=1}^m p^{i,i}_z - p^{i,j}_z \ge \mu
    \\
    %     & \;\; \forall \; i \in [k], \forall \; z \in [m] \nonumber
    % \\
        & \;\; \forall \; i, j \in [k], i \neq j, \forall \; z \in [m] \nonumber
    \\
        & \;\; \qquad p^{i,i}_z \le \min \{ w_\text{max} x^{i}_z, \, w^{i}_z \}
    \\
        & \;\; \qquad p^{i,j}_z \ge \max \{ 0, \, w^{i}_z - w_\text{max}(1 - x^{j}_z) \}
    \\
        & \;\; \forall \; i \in [k] \quad \vw^\bot \le \vw^{i} \le \vw^\top \label{eq:wbounds2}
    \\
        & \;\; \forall \; i \in [k] \quad \vx^{i} \in \calX_{\text{feasible}} \nonumber
    \\
        & \;\; \forall \; i \in [k] \quad \veps^{i}_h \ge 0 \nonumber
%    \\
%        & \;\; \mu \ge 0 \nonumber
\end{align}
}
%
%which can be solved by any suitable MILP solver.

@@

We compare {\sc SetMargin} against three state-of-the-art Bayesian
approaches: i) the Bayesian approach from \cite{guo2010real},
selecting queries according to {\em restricted informed VOI} ({\sc
  riVOI}), a computationally efficient heuristic approximation of
value-of-information, and inference using TrueSkill$^{TM}$
\cite{HerbrichMG06} (an inference scheme based on expectation
propagation \cite{Minka01}); ii) the Bayesian framework of
\cite{viappiani2010optimal} using Monte Carlo methods (with 50,000 particles) for
Bayesian inference and asking choice queries (asking the user to
select its preferred item among a set of diplayed ones); the next
query is computed by performing a greedy optimization of {\em Expected
  Utility of a Selection} (hereafter just called {\sc EUS}), a
submodular quantity that can be used as a proxy for value of
information (giving strong approximate guarantees); iii) {\em Query
  Iteration} (referred as {\sc QI} below), also from
\cite{viappiani2010optimal}, an even faster query selection method
based on sampling a set of utility vectors, selecting the items that
maximize utility for each of the vector and forming a first proposal
for a query set. Then, a new set is computed by considering the
optimal items in the associated beliefs, and the process is repeated
until convergence.

@@

\FloatBarrier

>>>>

Substituting the above MILP constraints into the original non-linear
formulation, we obtain the following mixed-integer linear problem:
%
{\footnotesize
\begin{align}
    \max
        & \;\; \mu - \alpha \sum_{i=1}^k \| \veps^{i} \|_1 - \beta \sum_{i=1}^k \| \vw^{i} \|_1 + \gamma \sum_{i=1}^k \sum_{z=1}^m p^{i,i}_z
        \nonumber
    \\
    \text{s.t.}
        & \;\; \forall \; i \in [k], \forall \; h \in [n] \quad \langle \vw^{i}, \vy^{h}_+ - \vy^{h}_- \rangle \ge \mu - \varepsilon^{i}_h \nonumber
    \\
        & \;\; \forall \; i, j \in [k], i \neq j \quad \sum_{z=1}^m p^{i,i}_z - p^{i,j}_z \ge \mu
    \\
    %     & \;\; \forall \; i \in [k], \forall \; z \in [m] \nonumber
    % \\
        & \;\; \forall \; i, j \in [k], i \neq j, \forall \; z \in [m] \nonumber
    \\
        & \;\; \qquad p^{i,i}_z \le \min \{ w_\text{max} x^{i}_z, \, w^{i}_z \}
    \\
        & \;\; \qquad p^{i,j}_z \ge \max \{ 0, \, w^{i}_z - w_\text{max}(1 - x^{j}_z) \}
    \\
        & \;\; \forall \; i \in [k] \quad \vw^\bot \le \vw^{i} \le \vw^\top \label{eq:wbounds2}
    \\
        & \;\; \forall \; i \in [k] \quad \vx^{i} \in \calX_{\text{feasible}} \nonumber
    \\
        & \;\; \forall \; i \in [k] \quad \veps^{i}_h \ge 0 \nonumber
%    \\
%        & \;\; \mu \ge 0 \nonumber
\end{align}
}
%
which can be solved by any suitable MILP solver.

@@

We compare {\sc SetMargin} against three state-of-the-art Bayesian
approaches: i) the Bayesian approach from \cite{guo2010real},
selecting queries according to {\em restricted informed VOI} ({\sc
  riVOI}), a computationally efficient heuristic approximation of
value-of-information, and inference using TrueSkill$^{TM}$
\cite{HerbrichMG06} (an inference scheme based on expectation
propagation \cite{Minka01}); ii) the Bayesian framework of
\cite{viappiani2010optimal} using Monte Carlo methods (with 50,000
particles) for Bayesian inference and asking choice queries
(i.e. selection of the most preferred item in a set) selected
optimizing {\em Expected Utility of a Selection} (a tight
approximation for the value of information, hereafter just called {\sc
  EUS}); iii) {\em Query Iteration} (referred as {\sc QI} below), also
from \cite{viappiani2010optimal}, an even faster query selection
method which repeateadly samples a set of utility vectors according to
their beliefs and forms a query set selecting the items that maximize
utility for each of the vectors.

@@
